### 2019-01-09 paper/sex_selection_spacing-ver2.tex
Minor edits

Finally, across surveys, the same cohort tends to show a higher sex ratio the more recent 
the survey (births in the cohort took place earlier relatively to the survey date).
Despite this, few cohorts show significantly different sex ratios across surveys, most 
likely because of a lack of power.
The exception is that comparisons involving NFHS-4 are mostly statistically significant
since the number of surveyed households in NFHS-4 were much larger than in prior surveys.

@@

The relationship between length of marriage and recall error can also seen in 
Figures \ref{fig:sex_ratio_recall_rounds_bo1} and \ref{fig:sex_ratio_recall_rounds_bo2}, 
which show the observed sex ratio for children reported as first born as a function of 
duration of marriage at the time of the survey.
The solid line is the sex ratio of children reported as first born by the number of years 
between the survey and marriage, the dashed lines indicate the 95 percent confidence 
interval and the horizontal line the natural sex ratio (approximately 0.512).
To ensure sufficient cell sizes the years are grouped in twos.
In line with the results from Tables \ref{tab:recallMarriageBO1} and 
\ref{tab:recallMarriageBO2}, the observed ratio of boys is increasingly above the expected 
value the longer ago the parents were married.

@@

The increasingly unequal sex ratio with increasing marriage duration suggests that
a solution to the recall error problem is to drop observations for 
women who were married ``too far'' from the survey year.
The main problem is establishing what the best cut-off point should be, with the
trade-off between retaining enough observations and the correctness of the information.
As Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2} show, there are 
differences in recall error across the three surveys and between parities, although
this may simply be the result of differences in number of observations across surveys.
Furthermore, the recall error pattern is not entirely consistent across observed birth 
orders.
Since most of the surveys start showing significantly biased sex ratio from around 22
years of marriage on, I drop all observations where the marriage took place 22 years
or more.

>>>>

Finally, across surveys, the same cohort tends to show a higher sex ratio the more recent 
the survey (births in the cohort took place earlier relative to the survey date).
Despite this, few cohorts show significantly different sex ratios across surveys, most 
likely because of a lack of power.
The exception is that comparisons involving NFHS-4 are mostly statistically significant
since the number of surveyed households in NFHS-4 were much larger than in prior surveys.

@@

The relationship between the length of marriage and recall error can also be seen in 
Figures \ref{fig:sex_ratio_recall_rounds_bo1} and \ref{fig:sex_ratio_recall_rounds_bo2}, 
which show the observed sex ratio for children reported as first born as a function of 
the duration of marriage at the time of the survey.
The solid line is the sex ratio of children reported as first-born by the number of years 
between the survey and marriage, while the dashed lines indicate the 95 percent confidence 
interval and the horizontal line the natural sex ratio (approximately 0.512).
To ensure sufficient cell sizes I group years into twos.
In line with the results from Tables \ref{tab:recallMarriageBO1} and 
\ref{tab:recallMarriageBO2}, the observed ratio of boys is increasingly above the expected 
value the longer ago the parents were married.

@@

The increasingly unequal sex ratio with increasing marriage duration suggests that
a solution to the recall error problem is to drop observations for 
women who were married ``too far'' from the survey year.
The main problem is establishing what the best cut-off point should be, with the
trade-off between retaining enough observations and the correctness of the information.
As Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2} show, there are 
differences in recall error across the three surveys and between the two birth
orders, although this may be the result of differences in the number of observations 
across surveys.
Furthermore, the recall error pattern is not entirely consistent across observed birth 
orders.
Since most of the surveys start showing significantly biased sex ratio from around 22
years of marriage on, I drop all observations where the marriage took place 22 years
or more.
